---
title: "Accelerometer_Processing_Simplified"
author: "Stephanie Wilson"
date: "April 19, 2023"
output: pdf_document
---

# Accelerometer Processing Script

Please refer to [README](https://github.com/SWi1/AccelerometerProcessing/blob/main/README.md) for additional start-up details.

**Key Construction**
A key for each file to be processed needs to be constructed. The general format requires:

  - path: the file path in the working directory
  - id_full: all identifying information related to the file
  - time_short: an abbreviation of the time (can also be a condition abbreviation, ie C or E)
  - time: an explanation of time (can also be a condition explanation, ie,     Control or Experimental)
  - id: study abbreviation with participant number


## Load packages and processing function
```{r}
library(tidyverse); library(readxl)
source('Process_Accelerometer_Function.R')
```

## Process A Singular File

**KEY STEP**: For your file of interest, complete information for each of the variables in the following dataframe. Entries must be kept in quotes.
```{r}
single_run = data.frame(id = 'P1', time = 'Pre', path = 'P1A_data.xlsx', time_short = 'A', id_full = 'P1A')
```

Run the function on one file
```{r warning = FALSE}
#Process File
processed = process_accel(id = id, time = time, path = path, data = single_run)
processed
```

Export Output
```{r}
output_path = paste(single_run$id_full, '_accelerometer_processed.csv', 
                    sep = '')

write.csv(processed, output_path, row.names = FALSE)
```

