---
title: "Accelerometer_Processing_Simplified"
author: "Stephanie Wilson"
date: "April 19, 2023"
output: pdf_document
---

# Accelerometer Processing Script

**Information** - This script automates the processing of accelerometer files from the Actigraph software. This scripts assumes the software output is an excel file with variable names that do not change and that all Excel naming follows the same naming convention. Additionally, to ensure script function, the following files need to be present in the same folder.

  - Accelerometer_Processing_Simple.Rmd
  - Process_Accelerometer_Function.R
  - Accelerometer Excel File (with a similar naming convention)

**Key Construction**
A key for each file to be processed needs to be constructed. The general format requires:

  - path: the file path in the working directory
  - id_full: all identifying information related to the file
  - time_short: an abbreviation of the time (can also be a condition abbreviation, ie C or E)
  - time: an explanation of time (can also be a condition explanation, ie,     Control or Experimental)
  - id: study abbreviation with participant number

**Output**  
Expected output is a csv file with only one row representing participant data and columns are accelerometer variables.


## Load packages and processing function
```{r}
library(tidyverse); library(readxl)
source('Process_Accelerometer_Function.R')
```

## Process A Singular File

**KEY STEP**: For your file of interest, complete information for each of the variables in the following dataframe. Entries must be kept in quotes.
```{r}
single_run = data.frame(id = 'P1', time = 'Pre', path = 'P1A_data.xlsx', time_short = 'A', id_full = 'P1A')
```

Run the function on one file
```{r warning = FALSE}
#Process File
processed = process_accel(id = id, time = time, path = path, data = single_run)
processed
```

Export Output
```{r}
output_path = paste(single_run$id_full, '_accelerometer_processed.csv', 
                    sep = '')

write.csv(processed, output_path, row.names = FALSE)
```

