---
title: "Accelerometer_Processing_Simplified"
author: "Stephanie Wilson"
date: "April 19, 2023"
output: pdf_document
---

# Accelerometer Processing Script
Please refer to [README](https://github.com/SWi1/AccelerometerProcessing/blob/main/README.md) for additional start-up details.

## Key Construction
A key for each file to be processed needs to be constructed. The general format requires:

  - path: the file path in the working directory
  - id_full: all identifying information related to the file
  - time_short: an abbreviation of the time (can also be a condition abbreviation, ie C or E)
  - time: an explanation of time (can also be a condition explanation, ie,     Control or Experimental)
  - id: study abbreviation with participant number

**Note**: If using conditions instead of time, adjustments will likely need to be made in the batch run code for string handling.


## Load packages and processing function
```{r}
library(tidyverse); library(readxl)
source('Process_Accelerometer_Function.R')
```


## Batch Run Files
Create a dataframe with data on files to be processed.
```{r}
filelist = data.frame(list.files(pattern = ".*.xlsx")) %>% #Grab all .xlsx files
  rename('path' = 1) %>%
  mutate(id_full = str_replace_all(path, '_data.xlsx', ''), # Remove path data
         time_short = str_sub(id_full, start =-1), #Isolate time
         time = ifelse(time_short == 'A', 'Pre', 'Post'), #Reformat Time
         id = substring(id_full, 1, nchar(id_full) -1)) #removes the last character from each string
       #  path = paste('\'', path, '\''))
```


Create Loop to Batch Run Every Excel File
```{r warning = FALSE}
finaloutput = data.frame()

for(i in 1:nrow(filelist)){
  
  # Part I - filter
  input = filelist[i, ]
  
  # Part II - Run function to process accelerometer files
  output = process_accel(time = time, id = id, path = path, data = filelist[i,])
 
  #Merge
  finaloutput = rbind(finaloutput, output)
}
```

Export Output
```{r}
write.csv(finaloutput, 'Accelerometer_long.csv', row.names = FALSE)
```

